MINOS Handover Plots

### 2023-07-18 minos/validation/cross_validation_default.Rmd
Added some dependencies to Rmd files to make them work in console and Rstudio

require(tidyverse)
require(ggplot2)
require(ggExtra)
require(here)
require(scales)

@@

```{r}

```

>>>>

require(tidyverse)
require(ggplot2)
require(ggExtra)
require(here)
require(scales)
require(dplyr)
require(tidyr)
require(purrr)

@@

## Parity

```{r}
cv.parity <- cv %>%
  filter(sex == "Female")

cv1.parity <- cv1 %>%
  filter(sex == "Female")

cv2.parity <- cv2 %>%
  filter(sex == "Female")

cv3.parity <- cv3 %>%
  filter(sex == "Female")

cv4.parity <- cv4 %>%
  filter(sex == "Female")

cv5.parity <- cv5 %>%
  filter(sex == "Female")

raw.parity <- raw %>%
  filter(sex == "Female")

cv.mean.plots(cv1.parity, cv2.parity, cv3.parity, cv4.parity, cv5.parity, raw.parity, 'nkids_ind')
multi_year_boxplots(raw.parity, cv.parity, 'nkids_ind')
q_q_comparison(raw.parity, cv.parity, 'nkids_ind')
```
```{r}
parity.pivoted <- combine_and_pivot_long(df1 = cv.parity,
                                         df1.name = 'simulated',
                                         df2 = raw.parity,
                                         df2.name = 'raw',
                                         var = 'nkids_ind')

cv_ordinal_plots(pivoted.df = parity.pivoted, 
                 var = 'nkids_ind',
                 save = FALSE)

rm(parity.pivoted)
```

### 2023-07-18 minos/validation/handovers.Rmd
Added some dependencies to Rmd files to make them work in console and Rstudio

require(tidyverse)
require(ggplot2)
require(ggridges) # for densities over time plots. 
require(knitr)
require(here)

@@

spaghetti_plot(income.spag, 'hh_income',
               save = shall.we.save,
               save.path = save.path)
density_ridges(income.spag, 'hh_income',
               save=TRUE, 
               save.path=save.path)

@@

density_ridges(sf12.spag, "SF_12", 
               save = T, 
               save.path = save.path)

@@

```{r}

```

>>>>

require(tidyverse)
require(ggplot2)
require(knitr)
require(here)
require(dplyr)
require(tidyr)
require(purrr)

@@

spaghetti_plot(income.spag, 'hh_income',
               save = shall.we.save,
               save.path = save.path)

@@

@@

## Parity

```{r}
base.parity <- base.dat %>%
  filter(sex == "Female")

raw.parity <- raw.dat %>%
  filter(sex == "Female")

prepped.list <- validation_prep_ordinal(raw.parity, base.parity, 'nkids_ind')

tit <- 'Parity (total no. of children)'

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = nkids_ind, colour = nkids_ind)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=nkids_ind)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'parity.png',
         plot = last_plot(),
         path = save.path)
}

rm(prepped.list, var, norm, tit)
```
```{r}
pivoted <- combine_and_pivot_long(df1 = base.parity,
                                  df1.name = 'simulated', 
                                  df2 = raw.parity, 
                                  df2.name = 'raw', 
                                  var = 'nkids_ind')

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'nkids_ind',
                 save = shall.we.save,
                 save.path = save.path)
```

```{r}
raw.s <- raw.parity %>%
  select(pidp, age, time, nkids_ind)
base.s <- base.parity %>%
  select(pidp, age, time, nkids_ind)

spaghetti_plot(spag, 'nkids_ind',
               save = shall.we.save,
               save.path = save.path)

```{r}
raw.s <- raw.parity %>%
  select(pidp, age, time, nkids_ind_raw)
base.s <- base.parity %>%
  select(pidp, age, time, nkids_ind_raw)

spaghetti_plot(spag, 'nkids_ind_raw',
               save = shall.we.save,
               save.path = save.path)
